---
title: "Exploratory Factor Analysis for R Workshop Survey Data"
author: "Aboli Marathe"
output: html_document
---

# Part 1: Setting up Environment
```{r echo=TRUE, message=FALSE, warning=FALSE}

#install.packages("psych")
library("psych")
#install.packages("GPArotation")
library("GPArotation")
```


# Part 2: Loading Dataset for Analysis
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Reading Cleaned Data from csv or xls
setwd("C:/Users/Aboli/Desktop/FOSSEE/Code")
df <- read.csv("cleaned_overall.csv")
df <- subset(df,select = -c(1))
df <- data.frame(apply(df, 2, function(x) as.numeric(as.character(x))))
length(colnames(df))
head(df)
```


# Part 3: Detecting and Removing Outliers
```{r echo=TRUE, message=FALSE, warning=FALSE}
#Calculating the mahalnobis values
mh_val = mahalanobis(df, colMeans(df, na.rm = T),cov(df, use = "pairwise.complete.obs"))

#cutoff score
cutoff = qchisq(1-.001, ncol(df))
cutoff

#Finding the number of outliers
summary(mh_val < cutoff)

#Removing outliers
noout = subset(df, mh_val < cutoff)
head(noout)
```

# Part 4: Correlation Analysis
```{r echo=TRUE, message=FALSE, warning=FALSE}
#Additivity test
corr_df = cor(df,use = "pairwise.complete.obs")
corr_df
```


# Part 5: Fake Regression Analysis
## Running the fake regression and creating standardized residuals. Creating the fitted values.
```{r echo=TRUE, message=FALSE, warning=FALSE}
#Fake regression analysis
random = rchisq(nrow(df), 7) 
fake = lm(random~., data = df)
standardized = rstudent(fake)
fitted = scale(fake$fitted.values)
```

## Normality test
```{r echo=TRUE, message=FALSE, warning=FALSE}
#normality
myplot <- hist(standardized)
myplot

```

## Linearity test
```{r echo=TRUE, message=FALSE, warning=FALSE}
#linearity
myplot <-qqnorm(standardized)
abline(0,1)
myplot
```

## Homogeneity and Homoscedasticity test
```{r echo=TRUE, message=FALSE, warning=FALSE}
#homogeneity
myplot <- plot(fitted,standardized)
abline(0,0)
abline(v = 0)
myplot
```

# Part 6: Bartlett and KMO test
```{r echo=TRUE, message=FALSE, warning=FALSE}
#Bartlett test
correl = cor(df, use = "pairwise.complete.obs")
cortest.bartlett(correl, n = nrow(df))


#KMO test
KMO(correl)

```

# Part 7: Factor analysis
## Determining ideal number of factors  for fa using Scree plot, old and new Kaiser Criterion.
```{r echo=TRUE, message=FALSE, warning=FALSE}

#the elbow in scree  plot shows how many factors are needed
nofactors = fa.parallel(noout, fm="ml", fa="fa")

#Kaiser criterion
sum(nofactors$fa.values > 1.0) ##old kaiser criterion
sum(nofactors$fa.values > .7) ##new kaiser criterion
```


## Conducting and visualizing factors.
```{r echo=TRUE,  fig.height=32, fig.width=20,message=FALSE, warning=FALSE}

#Factor analysis using maximum likelihood
round1 = fa(noout, nfactors=2, rotate = "oblimin", fm = "ml")
round1

# Rotation is set to promax
factanal(noout, factors = 2, rotation = "promax")

#visualize the factors
fa.diagram(round1)
```
