---
title: "CFA Analysis of  Live Session Feedback"
author: "Aboli Marathe"
output: html_document
---

# Part 1: Setting up Environment
```{r echo=TRUE, message=FALSE, warning=FALSE}

#install.packages("lavaan")
library("lavaan")
#install.packages("semPlot")
library("semPlot")
library("knitr")
library("ggplot2")
library("car")
```

# Part 2: Data Loading and Processing
```{r echo=TRUE, message=FALSE, warning=FALSE}
setwd("C:/Users/Aboli/Desktop/FOSSEE/Code")
df <- read.csv("cleaned_live.csv")
df <- subset(df,select = -c(1))
df <- data.frame(apply(df, 2, function(x) as.numeric(as.character(x))))
#Renaming column names because they look messy in the diagram
t <- c(paste("a",1:length(colnames(df)), sep = ""))
colnames(df) <- t
head(df)
```

# Part 3: Define  model
```{r echo=TRUE, message=FALSE, warning=FALSE}
#So we need to create the model and pass our features to it. Here we are fitting it to a simple structure using our general knowledge. 
wisc.model1 <- '
basic =~   a1 + a3 + a5 + a7 + a8 + a9 +  a2 + a4 + a6'

```

# Part 4: Fitting model
```{r echo=TRUE, message=FALSE, warning=FALSE}
fit1 <- lavaan::cfa(wisc.model1, df,std.lv=TRUE)
summary(fit1, fit.measures=T,standardized=T)
```

# Part 5: Obtain coefficients
```{r echo=TRUE, message=FALSE, warning=FALSE}
# obtain only the coefficients
kable(coef(fit1), booktabs=TRUE, format="markdown")

```

# Part 6: Complete parameter listing
```{r echo=TRUE, message=FALSE, warning=FALSE}
parameterEstimates(fit1,standardized=T)

```



# Part 7: Residuals correlation matrix
```{r echo=TRUE, message=FALSE, warning=FALSE}
cor_table <- residuals(fit1, type = "cor")$cov
#cor_table[upper.tri(cor_table)] <- # erase the upper triangle
#diag(cor_table) <- NA # erase the diagonal 0's
knitr::kable(cor_table, digits=3,format="markdown", booktabs=TRUE) # makes a nice table and rounds ever
```

# Part 8: Plot the residuals
```{r echo=TRUE, message=FALSE, warning=FALSE}
# extract the residuals from the fit1 model
# get rid of the duplicates and diagonal values
# create a vector for a
res1 <- residuals(fit1, type = "cor")$cov
res1[upper.tri(res1,diag=T)] <- NA
v1 <- as.vector(res1)
v2 <- v1[!is.na(v1)]
qqPlot(v2,id=F)
```

# Part 9: Modification Indices
```{r echo=TRUE, message=FALSE, warning=FALSE}
kable(modificationIndices(fit1, sort.=TRUE, minimum.value=3), booktabs=TRUE, format="markdown")

```


# Part 10: Path Diagram for the unifactor Model 1
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Note that the base plot, including standardized path coefficients plots positive coefficients green
# and negative coefficients red. Red-green colorblindness issues anyone?
# I redrew it here to choose a blue and red. But all the coefficients in this example are
# positive,so they are shown with the skyblue.
# more challenging to use colors other than red and green. not in this doc
semPaths(fit1, residuals=F,sizeMan=7,"std",
posCol=c("skyblue4", "red"),
#edge.color="skyblue4",
edge.label.cex=1.2,layout="circle2")

```

# Part 11: Visualization including residuals
```{r echo=TRUE, message=FALSE, warning=FALSE}
# or we could draw the paths in such a way to include the residuals:
#semPaths(fit1, sizeMan=7,"std",edge.color="skyblue4",edge.label.cex=1,layout="circle2")
# the base path diagram can be drawn much more simply:
#semPaths(fit1)
# or
semPaths(fit1,"std")
```

# Part 12:  Orthognal Fit Comparison
```{r echo=TRUE, message=FALSE, warning=FALSE}
fit1orth <- lavaan::cfa(wisc.model1, data=df,orthogonal=T)
kable(anova(fit1,fit1orth), booktabs=TRUE, format="markdown")

```

# Part 13: Results Interpretation

All the features seem to belong to the equally.  The same analysis carried out on a bifactor model yields similar results, which brings us to question the effectiveness of cfa on this dataset.



# References
Confirmatory Factor Analysis with R A Draft document using lavaan, sem, and OpenMx - Bruce Dudek